trials

### 2016-07-03 finalwriteup/trial_code.rmd
trial code for graphs

```{r, echo = FALSE, fig.cap = c("Distribution of the difference in RMSE between ANOVA model predictions (built on 6 core variables) and a base line predictor that uses the mean return per dollar as its prediction. If the ANOVA model is effective, the difference should be greater than 0.")}

#plot histogram to show differences
results.core %>% ggplot(., aes(x =diff, y = ..density..))+ 
        geom_histogram() + geom_density() +
        labs(x = "Difference in RMSE (Mean RMSE - Model RMSE)", title = "Density Plot of change in RMSE for 100 ANOVA models- core variables only") +
        theme(panel.background = element_rect(fill = 'gray95'))

@@

```{r, echo = FALSE, fig.cap = c("Distribution of the difference in RMSE between ANOVA model predictions (built on all variables) and a base line predictor that uses the mean return per dollar as its prediction. If the ANOVA model is effective, the difference should be greater than 0.")}

#plot histogram to show differences
results.A2 %>% ggplot(., aes(x =diff, y = ..density..))+ 
        geom_histogram() + geom_density() +
        labs(x = "Difference in RMSE (Mean RMSE - Model RMSE)", title = "Density Plot of change in RMSE for 50 ANOVA models - all variables sampled") +
        theme(panel.background = element_rect(fill = 'gray95'))

@@

```{r, echo = FALSE, fig.cap = c("Distribution of the difference in RMSE between randomForest predictions (built on 6 core variables) and a base line predictor that uses the mean return per dollar as its prediction. If the ANOVA model is effective, the difference should be greater than 0.")}

#plot histogram to show differences
results.rf.core %>% ggplot(., aes(x =diff, y = ..density..))+ 
        geom_histogram() + geom_density() +
        labs(x = "Difference in RMSE (Mean RMSE - Model RMSE)", title = "Density Plot of change in RMSE for 50 randomForest models- core variables only") +
        theme(panel.background = element_rect(fill = 'gray95'))

@@

```{r, echo = FALSE, fig.cap = c("Distribution of the difference in RMSE between randomForest predictions (built on all variables) and a base line predictor that uses the mean return per dollar as its prediction. If the ANOVA model is effective, the difference should be greater than 0.")}

#plot histogram to show differences
results.rf2 %>% ggplot(., aes(x =diff, y = ..density..))+ 
        geom_histogram() + geom_density() +
        labs(x = "Difference in RMSE (Mean RMSE - Model RMSE)", title = "Density Plot of change in RMSE for 50 randomForest models - all variables sampled") +
        theme(panel.background = element_rect(fill = 'gray95'))

@@

```{r, echo = FALSE, fig.cap = c("Distribution of RMSE's of 'return per dollar' from 100 randomForest models built on random subsamples of the variables")}

#plot histogram of RMSE's
results.rf2 %>% ggplot(., aes(x =final.RMSE, y = ..density..))+ 
        geom_histogram() + geom_density() +
        labs(x = "RMSE", title = "Density Plot of RMSE for 100 randomForest models - Variables Randomly Sampled") +
        theme(panel.background = element_rect(fill = 'gray95'))

@@

```{r TP_plot, fig.cap = c("True positive and false negative rates for each blended method using a typical model from each - displayed as a bar graph.")}
conf.plot <- readRDS("conf_plot.rds")

@@

ggplot(conf.plot %>% filter(actual == "loss"), 
       aes(x = method, y = pc, fill = model.pred)) +
        geom_bar(stat = "identity", position = "stack", alpha = 0.7) +
        scale_fill_manual(values = c('red2','dodgerblue2'),
                          labels = c("FN: predicted as profit", "TP: predicted as loss"),
                          name = "Confusion \nMatrix Reference") +
        labs(x = "Method (Original or Blended)", y = "Percent of All Loss-Making Projects (%)",
             title = "Breakdown of True Positives and False Negatives for Loss-Making Jobs") +
        scale_x_discrete(labels = c("average" = "Simple Av",
                                      "orig.boost"= "Orig. BT",
                                      "orig.log" = "Orig. LR",
                                      "orig.rf" = "Orig. RF",
                                      "simp.log" = "Simple LR",
                                      "simp.boost" = "Simple BT",
                                      "comp.boost"= "Complex BT",
                                      "comp.rf"= "Complex RF",
                                      "FWLS" = "FWLS")) +
        theme(axis.text.x=element_text(angle=30, hjust=1))

@@

```{r TN_plot, fig.cap = c("True negative and false positive rates for each blended method using a typical model from each - displayed as a bar graph.")}

@@

ggplot(conf.plot %>% filter(actual == "profit"), 
       aes(x = method, y = pc, fill = model.pred)) +
        geom_bar(stat = "identity", position = "stack", alpha = 0.7) +
        scale_fill_manual(values = c('dodgerblue2','red2'),
                          labels = c("TN: predicted as profit", "FP: predicted as loss"),
                          name = "Confusion \nMatrix Reference") +
        labs(x = "Method (Original or Blended)", y = "Percent of All Profitable Projects (%)",
             title = "Breakdown of True Negatives and False Positives for Profitable Jobs") +
        scale_x_discrete(labels = c("average" = "Simple Av",
                                      "orig.boost"= "Orig. BT",
                                      "orig.log" = "Orig. LR",
                                      "orig.rf" = "Orig. RF",
                                      "simp.log" = "Simple LR",
                                      "simp.boost" = "Simple BT",
                                      "comp.boost"= "Complex BT",
                                      "comp.rf"= "Complex RF",
                                      "FWLS" = "FWLS")) +
        theme(axis.text.x=element_text(angle=30, hjust=1))

@@

ggplot(reject.plot, aes(x = f.rpdol)) +
        geom_bar(aes(y = (..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) +
        facet_wrap(~compare,
                   labeller = labeller(compare = 
                                        c("full" = "All Projects",
                                       "reject"= "Rejected Projects Only"))) + 
        scale_y_continuous(labels = scales::percent) +
        labs(x = "Project Performance", 
             y = "Relative Frequency",
             title = "Ratio of Profitable vs. Loss-Making Projects")

@@

```{r, fig.cap = c("Proportion of the absolute value of profits and losses from profitable and loss-making jobs in the rejected projects only. Colours are alternated between different jobs to indicate profit/loss magnitude. Predictions were from a typical simple Logistic Regression.")}
ggplot(reject.plot %>% filter(compare == "reject") %>% arrange(desc(abs(balance.mlsto))), 
             aes(x = f.rpdol, y = abs(balance.mlsto), fill = mlsto)) +
        geom_bar(stat = "identity") + 
        theme(legend.position="none") +
        scale_fill_manual(values = rep(c('dodgerblue4', 'darkolivegreen1'), 59)) + 
        scale_y_continuous(labels = scales::dollar) +
        labs(x = "Project Performance", 
             y = "Cumulative Profits/Losses",
             title = "Magnitude of Profits/Losses from Rejected Projects") +
        geom_text(data = NULL, x = .5, y = 720000, size = 3, 
                  colour = "gray60", hjust = 0,
                  label = "Alternate Colours \nIndicate Different \nProjects")

@@

```{r, fig.cap = c("Distribution of the percentage of hours completed by a professional level employee in the full data set of projects vs. the rejected projects only. Predictions from a typical simple Logistic Regression were used.")}
ggplot(reject.plot, 
             aes(x = pc.pro)) +
        geom_density() + 
        facet_wrap(~compare,
                   labeller = labeller(compare = 
                                        c("full" = "All Projects",
                                       "reject"= "Rejected Projects Only"))) +
        labs(x = "% of Hours Completed by Professional Level Employee", 
             y = "Density",
             title = "Density of Percentage of Hours by Professional Level Employees") 
```

```{r, fig.cap = c("Proportion of each timespan category for projects in the full data set vs. the rejected projects only. Predictions from a typical simple Logistic Regression were used.")}
ggplot(reject.plot, 
             aes(x = b.timespan.cbrt)) +
        geom_bar(aes(y = (..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) + 
        facet_wrap(~compare,
                   labeller = labeller(compare = 
                                        c("full" = "All Projects",
                                       "reject"= "Rejected Projects Only"))) +
        labs(x = "Timespan", 
             y = "Relative Frequency",
             title = "Relative Frequency of Project Timespans") + 
        theme(axis.text.x=element_text(angle=30, hjust=1))

@@

```{r, fig.cap = c("Distribution of 'return per dollar' in the full data set of projects vs. the rejected projects only. Predictions from a typical simple Logistic Regression were used.")}
ggplot(reject.plot, 
             aes(x = return.pdol)) +
        geom_density() + 
        facet_wrap(~compare,
                   labeller = labeller(compare = 
                                        c("full" = "All Projects",
                                       "reject"= "Rejected Projects Only"))) +
        labs(x = "Return per Dollar", 
             y = "Density",
             title = "Density Plots of Return per Dollar") +
        scale_x_continuous(labels = scales::dollar)
```

>>>>

```{r, fig.height = 4.3, fig.cap = c("Distribution of the difference in RMSE between ANOVA model predictions (built on 6 core variables) and a base line predictor that uses the mean return per dollar as its prediction. If the ANOVA model is effective, the difference should be greater than 0.")}

#plot histogram to show differences
results.core %>% ggplot(., aes(x =diff, y = ..density..))+ 
        geom_histogram() + geom_density() +
        labs(x = "Difference in RMSE (Mean RMSE - Model RMSE)", title = "Density Plot of change in RMSE for 100 ANOVA models \nCore Variables Only") +
        theme(panel.background = element_rect(fill = 'gray95'))

@@

```{r, fig.height = 4.3, echo = FALSE, fig.cap = c("Distribution of the difference in RMSE between ANOVA model predictions (built on all variables) and a base line predictor that uses the mean return per dollar as its prediction. If the ANOVA model is effective, the difference should be greater than 0.")}

#plot histogram to show differences
results.A2 %>% ggplot(., aes(x =diff, y = ..density..))+ 
        geom_histogram() + geom_density() +
        labs(x = "Difference in RMSE (Mean RMSE - Model RMSE)", title = "Density Plot of change in RMSE for 50 ANOVA models \nAll Variables Sampled") +
        theme(panel.background = element_rect(fill = 'gray95'))

@@

```{r, fig.height = 4.3, echo = FALSE, fig.cap = c("Distribution of the difference in RMSE between randomForest predictions (built on 6 core variables) and a base line predictor that uses the mean return per dollar as its prediction. If the ANOVA model is effective, the difference should be greater than 0.")}

#plot histogram to show differences
results.rf.core %>% ggplot(., aes(x =diff, y = ..density..))+ 
        geom_histogram() + geom_density() +
        labs(x = "Difference in RMSE (Mean RMSE - Model RMSE)", title = "Density Plot of change in RMSE for 50 randomForest models \nCore Variables Only") +
        theme(panel.background = element_rect(fill = 'gray95'))

@@

```{r, fig.height = 4.3, echo = FALSE, fig.cap = c("Distribution of the difference in RMSE between randomForest predictions (built on all variables) and a base line predictor that uses the mean return per dollar as its prediction. If the ANOVA model is effective, the difference should be greater than 0.")}

#plot histogram to show differences
results.rf2 %>% ggplot(., aes(x =diff, y = ..density..))+ 
        geom_histogram() + geom_density() +
        labs(x = "Difference in RMSE (Mean RMSE - Model RMSE)", title = "Density Plot of change in RMSE for 50 randomForest models \nAll Variables Sampled") +
        theme(panel.background = element_rect(fill = 'gray95'))

@@

```{r, fig.height = 4.3, echo = FALSE, fig.cap = c("Distribution of RMSE's of 'return per dollar' from 100 randomForest models built on random subsamples of the variables")}

#plot histogram of RMSE's
results.rf2 %>% ggplot(., aes(x =final.RMSE, y = ..density..))+ 
        geom_histogram() + geom_density() +
        labs(x = "RMSE", title = "Density Plot of RMSE for 100 randomForest models \nVariables Randomly Sampled") +
        theme(panel.background = element_rect(fill = 'gray95'))

@@

```{r TP_plot, fig.height = 5, fig.cap = c("True positive and false negative rates for each blended method using a typical model from each - displayed as a bar graph.")}
conf.plot <- readRDS("conf_plot.rds")

@@

ggplot(conf.plot %>% filter(actual == "loss"), 
       aes(x = method, y = pc, fill = model.pred)) +
        geom_bar(stat = "identity", position = "stack", alpha = 0.7) +
        scale_fill_manual(values = c('red2','dodgerblue2'),
                          labels = c("FN: predicted as profit", "TP: predicted as loss"),
                          name = "Confusion Matrix Reference") +
        labs(x = "Method (Original or Blended)", y = "Percent of All Loss-Making Projects (%)",
             title = "Breakdown of True Positives and False Negatives for Loss-Making Jobs") +
        scale_x_discrete(labels = c("average" = "Simple Av",
                                      "orig.boost"= "Orig. BT",
                                      "orig.log" = "Orig. LR",
                                      "orig.rf" = "Orig. RF",
                                      "simp.log" = "Simple LR",
                                      "simp.boost" = "Simple BT",
                                      "comp.boost"= "Complex BT",
                                      "comp.rf"= "Complex RF",
                                      "FWLS" = "FWLS")) +
        theme(axis.text.x=element_text(angle=30, hjust=1),
              legend.position = "bottom")

@@

```{r TN_plot, fig.height = 5, fig.cap = c("True negative and false positive rates for each blended method using a typical model from each - displayed as a bar graph.")}

@@

ggplot(conf.plot %>% filter(actual == "profit"), 
       aes(x = method, y = pc, fill = model.pred)) +
        geom_bar(stat = "identity", position = "stack", alpha = 0.7) +
        scale_fill_manual(values = c('dodgerblue2','red2'),
                          labels = c("TN: predicted as profit", "FP: predicted as loss"),
                          name = "Confusion Matrix Reference") +
        labs(x = "Method (Original or Blended)", y = "Percent of All Profitable Projects (%)",
             title = "Breakdown of True Negatives and False Positives for Profitable Jobs") +
        scale_x_discrete(labels = c("average" = "Simple Av",
                                      "orig.boost"= "Orig. BT",
                                      "orig.log" = "Orig. LR",
                                      "orig.rf" = "Orig. RF",
                                      "simp.log" = "Simple LR",
                                      "simp.boost" = "Simple BT",
                                      "comp.boost"= "Complex BT",
                                      "comp.rf"= "Complex RF",
                                      "FWLS" = "FWLS")) +
        theme(axis.text.x=element_text(angle=30, hjust=1),
              legend.position = "bottom")

@@

ggplot(reject.plot, aes(x = f.rpdol)) +
        geom_bar(aes(y = (..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) +
        facet_wrap(~compare,
                   labeller = labeller(compare = 
                                        c("full" = "All Projects",
                                       "reject"= "Rejected Projects Only"))) + 
        scale_y_continuous(labels = scales::percent) +
        labs(x = "Project Performance", 
             y = "Relative Frequency",
             title = "Ratio of Profitable vs. Loss-Making Projects") +
        theme(panel.background = element_rect(fill = 'gray95'))

@@

```{r, fig.height = 5, fig.cap = c("Proportion of the absolute value of profits and losses from profitable and loss-making jobs in the rejected projects only. Colours are alternated between different jobs to indicate profit/loss magnitude. Predictions were from a typical simple Logistic Regression.")}
ggplot(reject.plot %>% filter(compare == "reject") %>% arrange(desc(abs(balance.mlsto))), 
             aes(x = f.rpdol, y = abs(balance.mlsto), fill = mlsto)) +
        geom_bar(stat = "identity") + 
        theme(legend.position="none") +
        scale_fill_manual(values = rep(c('dodgerblue4', 'darkolivegreen1'), 59)) + 
        scale_y_continuous(labels = scales::dollar) +
        labs(x = "Project Performance", 
             y = "Cumulative Profits/Losses",
             title = "Magnitude of Profits/Losses from Rejected Projects") +
        geom_text(data = NULL, x = .5, y = 720000, size = 3, 
                  colour = "gray60", hjust = 0,
                  label = "Alternate Colours \nIndicate Different \nProjects")

@@

```{r, fig.cap = c("Distribution of the percentage of hours completed by a professional level employee in the full data set of projects vs. the rejected projects only. Predictions from a typical simple Logistic Regression were used.")}
ggplot(reject.plot, 
             aes(x = pc.pro)) +
        geom_density() + 
        facet_wrap(~compare,
                   labeller = labeller(compare = 
                                        c("full" = "All Projects",
                                       "reject"= "Rejected Projects Only"))) +
        labs(x = "% of Hours Completed by Professional Level Employee", 
             y = "Density",
             title = "Density of Percentage of Hours by Professional Level Employees") +
        theme(panel.background = element_rect(fill = 'gray95'))
```

```{r, fig.cap = c("Proportion of each timespan category for projects in the full data set vs. the rejected projects only. Predictions from a typical simple Logistic Regression were used.")}
ggplot(reject.plot, 
             aes(x = b.timespan.cbrt)) +
        geom_bar(aes(y = (..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) + 
        facet_wrap(~compare,
                   labeller = labeller(compare = 
                                        c("full" = "All Projects",
                                       "reject"= "Rejected Projects Only"))) +
        labs(x = "Timespan", 
             y = "Relative Frequency",
             title = "Relative Frequency of Project Timespans") + 
        theme(axis.text.x=element_text(angle=30, hjust=1),
              panel.background = element_rect(fill = 'gray95'))

@@

```{r, fig.cap = c("Distribution of 'return per dollar' in the full data set of projects vs. the rejected projects only. Predictions from a typical simple Logistic Regression were used.")}
ggplot(reject.plot, 
             aes(x = return.pdol)) +
        geom_density() + 
        facet_wrap(~compare,
                   labeller = labeller(compare = 
                                        c("full" = "All Projects",
                                       "reject"= "Rejected Projects Only"))) +
        labs(x = "Return per Dollar", 
             y = "Density",
             title = "Density Plots of Return per Dollar") +
        scale_x_continuous(labels = scales::dollar) +
        theme(panel.background = element_rect(fill = 'gray95'))
```
